---
title: "Introduction to cdsamplr package"
author: "Hannah Patterson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Background
The cdsamplr package provides functions that allow for sampling from continuous random variable distributions.

## Rejection Sampling
The idea behind rejection sampling is to:
a. test the location of values that are uniformly and randomly sampled 
b. keep values that fall under the region of the probability density funciton
c. reject values that fall outside of the region of the probability density function

How it is done:
1. start with a proposed sample from a uniform distribution between a and b
2. select a critical value by using a uniform distribution between 0 and C (where    C is the maximum of the density function)
3. compute the pdf of the critical value
4. compare the proposed sample to the pdf of the critical value
5. if the proposed is less than the critical value, store the proposed in a vector

## Example - Rejection Sampling Uniform 

Here is an example of Rejection_Samplr using the uniform distribution.

```{r}
 sim_data <- rejection_samplr(1300, dunif, 0,1,2)
 hist(sim_data, probability = TRUE)
```

## Example - Rejection Sampling Custom PDF

Here is an example of Rejection_Samplr using a custom probability density function. 


```{r}
my_pdf <- function(x) {
  ifelse(x>=0 & x<=2, (x/2), 0)}

  sim_data <- rejection_samplr(30000, my_pdf, 0,2,1)
  hist(sim_data, probability = TRUE)
  curve(my_pdf(x), col = "red", add = TRUE)
```

## Example - Rejection Sampling Beta PDF

Here is an example of Rejection_Samplr using a beta probability density function. It has a set pdf where shape1 = 2 and shape2 = 3.

```{r}
sim_data <- rejection_samplr(1300, pdf_beta, a = 0,b = 1,C =1.5)
pdf_beta <- function(x) {
  dbeta(x, shape1 = 2, shape2 = 3)
}
hist(sim_data, probability = TRUE)
curve(dbeta(x,2,3), col = "red", add = TRUE)
```

