---
title: "Introduction to cdsamplr package"
author: "Hannah Patterson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Background
The cdsamplr package provides functions that allow for sampling from continuous random variable distributions.



## Rejection Sampling
The idea behind rejection sampling is to:
a. test the location of values that are uniformly and randomly sampled 
b. keep values that fall under the region of the probability density funciton
c. reject values that fall outside of the region of the probability density function

How it is done:
1. start with a proposed sample that from a uniform distribution between a and b
2. select a critical value by using the uniform distribution between 0 and C (where    C is the maximum of the density function)
3. compute the pdf of the critical value
4. compare the proposed sample to the pdf of the critical value
5. if the proposed is less than the critical value, store the proposed in a vector.

## Example - Rejection Sampling Uniform 

Here is an example of Rejection_Samplr using the uniform distribution.

```{r}
 sim_data <- rejection_samplr(1300, dunif, 0,1,2)
 hist(sim_data, probability = TRUE)
```



## Example - Rejection Sampling Custom PDF

Here is an exaple of Rejection_Samplr using a custom probability density function. 


```{r}
my_pdf <- function(x) {
  ifelse(x>=0 & x<=2, (x/2), 0)}
  sim_data <- rejection_samplr(30000, my_pdf, 0,2,1)
  hist(sim_data, probability = TRUE)
```
